---
title: "linear model from Web"
author: "Alondra Garcia"
date: "Summer 2022"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS




### scatterplot

```{r}
plot(SIMS~ARM,data=data)
lmr = lm(SIMS~ARM, data=data)
abline(lmr)
```

the graph has a strong positive affect 

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

the numerical result for the graph is 0.6860073

### Inferential  (Build model.1)

```{r}
summary(lmr)
newdata=c(GRIP=94, ARM=88)
```

The p-vaule for GRIP and ARM is 0.00000000000000022 with the median of -0.0285, with an R-square of 0.467, a min of-3.6467 and max of 3.0770.

#### Predict at target point

```{r}
predictSIMS=predict.lm(lmr, newdata= data.frame(GRIP=94, ARM=88))
print(predictSIMS)
```

the predicting number is 0.7063836

#### scatterplot with model fit
  
```{r}
plot(lmr)
```


## Model 2 SIM~GRIP

### Now add in scatterplot
```{r}
plot(SIMS~GRIP,data=data)
lmr = lm(SIMS~GRIP, data=data)
abline(lmr)
```

This graph shows a positive strong relationship towards the middle of the graph near the 100 mark. The graphs data is increasing.

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

the numerical result is 0.6398458

### Inferential  (Build model.2)
  
```{r}
summary(lmr)
newdata=c(SIMS=95, GRIP=94)
```

The p-vaule for SIMS and GRIP is 0.000000000000000022 with a min of -2.9295, median of -0.1219, and max of 3.3494. With R-square of 0.4053

#### predict model.2 at target point

#### now add the model fit to our plot for model.2


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
data2=lm(SIMS~ARM+GRIP, data=data)
summary(data2)
```
  
the p-vaule for this graph is 0.000000000000000022 with a R-square value of 0.5358. Min of -3.1846, median of -0.0641 and max of 2.8634  
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point

```{r}
predict.lm(data2,newdata= data.frame(GRIP=94, ARM=88))
```

predicting point for this graph is 0.1496476

## Comparing nested models ANOVA Test

### Model.1 vs Model.3

```{r}
anova(lmr, data2)
```

### Model.2 vs Model.3

```{r}
anova(lmr, data2)
```



## Informally compare Model.1 with model.2

